Dirac neutrino mass generation from Majorana messenger

### 2019-09-18 draft.tex
Updates from Overleaf

where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distribution, $g_{\nu_R} = 2$, $\upsilon = 1-\cos{\theta}$ is the Moller velocity, $s = 2 p k (1-\cos{\theta})$, $p$ and $k$ are the momenta of the particle with $\theta$ the angle between them, and the number density of right-handed neutrinos is given by

@@

%
\begin{figure}[t]
\centering
\includegraphics[scale=1]{D_Neff.pdf}
\caption{Contribution to the number of extra relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$. The region above the gray line is excluded by the measurements at $2\sigma$ from PLANCK~\cite{Aghanim:2018eyx}. The horizontal dashed lines show the projected sensitivity of the future experiments SPT-3G/SO~\cite{Benson:2014qhw} and CMB-S4~\cite{Abitbol:2019nhf}. }
\label{fig:Neff}
\end{figure}
%

@@

\begin{figure}
    \centering
    \includegraphics[scale=1.0]{u1blc}
    \caption{Collider and cosmological constraints for the $\operatorname{U}(1)_{B-L}$ model, and contours of constant $g'$ in the plane of $q_s v_S$ as a function of $M_{Z'}$ with $q_S=2$.}
    \label{fig:u1blc}
\end{figure}

@@

\section{Summary}

>>>>

where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distribution, $g_{\nu_R} = 2$, $\upsilon = 1-\cos{\varphi}$ is the Moller velocity, $s = 2 p k (1-\cos{\varphi})$, $p$ and $k$ are the momenta of the particle with $\varphi$ the angle between them, and the number density of right-handed neutrinos is given by

@@

%
\begin{figure}[t]
\centering
\includegraphics[scale=1]{D_Neff.pdf}
\caption{Contribution to the number of extra relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$. The region above the solid gray line is excluded by the measurements at $2\sigma$ reported by the PLANCK Collaboration~\cite{Aghanim:2018eyx}. For comparison purposes  the upper bound at $2\sigma$ (black line) obtained from the BBN analysis~\cite{Pitrou:2018cgg} is also shown.  The horizontal dashed lines show the projected sensitivity of the future experiments SPT-3G/SO~\cite{Benson:2014qhw} and CMB-S4~\cite{Abitbol:2019nhf}. $\Delta N_{\text{eff}}=0.4$ represents the extra contribution  required to relieve the tension on the inferred $H_0$ values from  high- and low-redshift observations \cite{Bernal:2016gxb,Mortsell:2018mfj}. }
\label{fig:Neff}
\end{figure}
%

@@

\begin{figure}[t]
    \centering
    \includegraphics[scale=1.0]{u1blc}
    \caption{Collider and cosmological constraints for the $\operatorname{U}(1)_{B-L}$ model, and contours of constant $g'$ in the plane of $q_S v_S$ as a function of $M_{Z'}$ with $q_S=3/2$.}
    \label{fig:u1blc}
\end{figure}

@@

\section{Summary}
The mechanism behind the neutrino mass generation and the Dirac/Majorana character of massive neutrinos still remain a conundrum despite the clear understanding of the neutrino oscillation pattern and the great experimental efforts behind the neutrinoless double-beta decay. Alongside this is the fact that there are no clues on the nature of the DM particle and the properties of the dark sector it belongs.

In view of this we have proposed a new mechanism for Dirac neutrino masses which making use of heavy Majorana mediators generate nonzero masses at one-loop level. 
The model presented in this paper is a one-loop realization of the dimension 6 operator $\overline{L} \tilde{H} \nu_R S^2\,$ and enters into the list of Dirac radiative type-I seesaw models with the novel feature that it involves Majorana mediators rather Dirac mediators. 
The Diracness of the massive neutrinos is protected by only one extra $\operatorname{U}(1)_X$ gauge symmetry, which in turn ensures the stability of the lightest particle mediating the one-loop neutrino mass diagram. In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.

We have illustrated our proposal by considering a specific
model, where simple numerical estimates allow us to show the effectiveness of the scheme regarding neutrino masses, DM and lepton flavor violating processes. Furthermore,.
